The Impact of Education <br>

### 2014-12-04 Presentation/EdEntrePres.Rmd
Final changes to presentatino

---
title: "The Impact of Education <br>
on Entrepreneurship"
author: "Sam Dundon and Thierry Racaud"
date: "December 2, 2014"
output: ioslides_presentation
---

@@

1. Education System that reinforces Self-confidence

@@

- GEM is being used is regularly refered to in research, including in OECD reports.

- GEM uses primary data collection which results in massive comprehensive datasets. That is the 2001-2010 multi-year APS Database covers over 1.3 million observations over 85 countries.

@@

Variable | Indicator 
-------------|---------------
Y Dependent Vaiable | Rate of Entrepreneurship (Intention, Nascent, Established)
X1 Explanatory Variable | Way of Teaching
X2 Control Variable | Perceived Capabilities
X3 Control Variable | Fear of Failure / Perceived Opportunities
X4 Control Variable | Perceived Opportunities

## Explaining Way of Teaching

@@

## Variation in how well Education encourages Self Confidence in OECD Countries

@@

## Variation in Impact of Education on Self Confidence
```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
library("ggplot2")
library("reshape2")

@@

- This figure is a national-level precentage

- This measure was chosen to provide some insight on how personal values are shaped, especially in terms of self-confidence.

## Differences in Perceived Capability in OECD Countries

@@

## Time Variation in Perceived Capabilities
```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
library("ggplot2")
library("reshape2")

@@

## Fear of Failure

@@

## Variation in Fear Perception in OECD Countries

@@

## Variation in Fear of Failure
```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
library("ggplot2")
library("reshape2")

@@

## Perceived Opportunities

@@

## Varying Perceptions of Good Opportunities to Start a Business in OECD Countries

@@

- We decided to do this because the coefficients do not change signficantly when the country-specific effects are ignored.

@@

```{r, echo =FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}

>>>>

---
title: "The Impact of Education <br>
on Entrepreneurship"
author: "Sam Dundon and Thierry Racaud"
date: "December 4, 2014"
output: ioslides_presentation
---

## Research Question

- To what extent do teaching methods supporting self confidence affect the rate of entrepreneurship in OECD countries?

@@

1. Education System that reinforces self-confidence

@@

- GEM is being used is regularly referred to in research, including in OECD reports.

- GEM uses primary data collection which results in massive comprehensive data sets. That is the 2001-2010 multi-year APS Database covers over 1.3 million observations over 85 countries.

@@

Variable | Indicator 
-------------|---------------
Y Dependent Variable | Rate of Entrepreneurship (Intention, Nascent, Established)
X1 Explanatory Variable | Way of Teaching
X2 Control Variable | Perceived Capabilities
X3 Control Variable | Fear of Failure / Perceived Opportunities
X4 Control Variable | Perceived Opportunities

## How Much the Way of Teaching Supports Self-Confidence

@@

## Variation in how the Way of Teaching is Perceived to Support Self-Confidence

@@

## Variation in Perceived Impact of the Way of Teaching on Self Confidence
```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
library("ggplot2")
library("reshape2")

@@

- This figure is a national-level percentage

- This measure was chosen to provide some insight on self-confidence at the country level

## Differences in Perceived Capabilities to start a Business

@@

## Variation in Perceived Capabilities to Start a Business
```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
library("ggplot2")
library("reshape2")

@@

## Fear of Failure Despite Good Perceived Opportunities

@@

## Variation in Fear of Failure Despite Perceived Good Opportunities

@@

## Variation in Fear of Failure Despite Good Perceived Opportunities
```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
library("ggplot2")
library("reshape2")

@@

## Perceived Good Opportunities to Start a Business

@@

## Varying Perceptions of Good Opportunities to Start a Business

@@

- We decided to do this because the coefficients do not change significantly when the country-specific effects are ignored.

@@

## Conclusions

- Some expected trends observed

- Inconclusive results

- Lack of reliable data
